Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-05-11 analysis/Manuscript/Paper_RFigures.Rmd
Update to BenMAP valuation results

```{r, countrymap}

#should these be per capita?
# add per capita code

## FIgure 2b and adapted to S5

#map of country mortality results
MODEL = 'HadGEM'

Plots <-file.path(getwd(),'Results','Global BenMAP WebTool')

countryResults <- read.csv(paste0(Plots,"/Country Results Summary by Model & Year_eem.csv"))

@@

#plot by super region?

#need to sum all country results

#map data
worldData <- map_data("world")
#correct region names
worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
worldData["region"][worldData["region"] == "USA"] <- "United States"
worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"

@@

#chloropleth of world
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = TotalResults),
               color = 'black',linewidth=0.15)+

#  scale_fill_binned("Total Deaths",
#                    breaks= c(0,100,1000,10000,80000),
#                    guide= guide_colorsteps(even.steps = FALSE))+
  scale_fill_fermenter("Total Deaths",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(0,100000),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       label=scales::comma)+#,
                       #guide =  guide_colorbar(nbin=10))+

@@

# Map of the world:
#p5<- map('world',col="grey", fill=TRUE, bg="white", lwd=0.05, mar=rep(0,4),border=0, ylim=c(-80,80) )

p5
ggsave(plot = p5, filename = 
         file.path(Plots,'Plots',paste0('Total_MortMap_',MODEL,'.png')),width = 9,height = 5)
```

```{r, countrymap_percapita}

#should these be per capita?
# add per capita code

@@

Plots <-file.path(getwd(),'Results','Global BenMAP WebTool')

countryResults <- read.csv(paste0(Plots,"/Country Results Summary by Model & Year_eem.csv"))
country_2020 <- countryResults %>%
  select(c('COUNTRY','Region','SuperRegion','Model','AvgResponse','X2020')) %>%
  filter(Model == MODEL) %>%
  rename(region = COUNTRY) #%>%

#read in population
inputs <- file.path("Code","InputData","Creating RFF Lookup Tables")
mean.pop<-read.csv(file.path(inputs,"rff_pop_means.csv")) #this dataset includes all countries (rff-sp does not)
mean.pop <- mean.pop %>%
  filter(Year ==2020) %>%
  mutate(mean_pop = mean_pop *1000) %>% #convert to ppl counts
  group_by(LocID) %>%
  summarise_at(.vars = c('mean_pop'), sum)

inputs3 <- file.path("Code","InputData","Tool Inputs")
Ctry.Name<-read.csv(file.path(inputs3,'Final Country Grid Col_Row Index_EEM.csv'))

@@

#read in mort data (created in the mortality timeseries chunk)
mort_rate <- resp_mort_means_noage %>% 
  filter(Min.Year ==2020)
country_plot <- country_plot1 %>% left_join(mort_rate, by ='LocID')

#plot by super region?

#need to sum all country results

#map data
worldData <- map_data("world")
#correct region names
worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
worldData["region"][worldData["region"] == "USA"] <- "United States"
worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"

@@

#chloropleth of world
# Percapita deaths
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = death_percap),
               color = 'black',linewidth=0.15)+
#  scale_fill_gradientn(
#   colors=c("red","white","blue"),
#   values=rescale(c(-1,0,1)),
#   limits=c(-1,1))+
  scale_fill_fermenter("Deaths Per Capita",
                       n.breaks=10.5,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       #values=rescale(c(-1,0,1)),
                       limits=c(#0,
                                min(MergedData$death_percap, na.rm=TRUE),
                                0.3),
                                #max(MergedData$death_percap, na.rm=TRUE)),
                       #midpoint=1,
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       #breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       #label=scales::comma)+#,
                       labels = c('Minimum',rep('',8),'Maximum'))+
                       #guide =  guide_colorbar(nbin=10))+

                       #guides() (fill= guide_colorbar(even.steps) = FALSE
  #scale_fill_continuous(name="Total Mortality (deaths per 100K)",
  #                      low="darkblue",
  #                      high="lightblue",
  #                      limits=c(0,70),
  #                      na.value='gray')+
  theme_void()+
  theme(legend.position = 'right')+
  theme(legend.key.height = unit(0.5,'cm'),
        legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  #ggtitle('Total Deaths Per 100K')+
  #theme(plot.title = element_text(size = 20))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))

# Map of the world:
#p5<- map('world',col="grey", fill=TRUE, bg="white", lwd=0.05, mar=rep(0,4),border=0, ylim=c(-80,80) )

>>>>

##Figure S5

global maps of respiratory mortality, absolute total (by model)
```{r, countrymap}

Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
input <- file.path(getwd(),'input','BenMAP')
countryResults <- read.csv(paste0(input,"/Country Results Summary by Model & Year.csv"))

@@

# load map data and align country names
worldData <- map_data("world")
#correct region names
worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
worldData["region"][worldData["region"] == "USA"] <- "United States"
worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"

@@

#chloropleth of world
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = TotalResults),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Total Deaths",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(0,100000),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       label=scales::comma)+#,
                       #guide =  guide_colorbar(nbin=10))+

@@

p5
ggsave(plot = p5, filename = 
         file.path(Plots,paste0('Total_MortMap_',MODEL,'.png')),width = 9,height = 5)
```

## Figures 2b and SXX

global maps of respiratory mortality, per capita (in 2020)
as well as maps of 2020 population, mortality rate, and average O3/CH4 response
```{r, countrymap_percapita}

@@

Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
input <- file.path(getwd(),'input')
countryResults <- read.csv(paste0(input,'/BenMAP',"/Country Results Summary by Model & Year.csv"))

country_2020 <- countryResults %>%
  select(c('COUNTRY','Region','SuperRegion','Model','AvgResponse','X2020')) %>%
  filter(Model == MODEL) %>%
  rename(region = COUNTRY) #%>%

#read in population
socio_inputs <- file.path('input','RFF','lookup_tables')
mean.pop<-read.csv(file.path(socio_inputs,"rff_pop_means.csv")) #this data set includes all countries (rff-sp does not)
mean.pop <- mean.pop %>%
  filter(Year ==2020) %>%
  mutate(mean_pop = mean_pop *1000) %>% #convert to ppl counts
  group_by(LocID) %>%
  summarise_at(.vars = c('mean_pop'), sum)

#inputs3 <- file.path("Code","InputData","Tool Inputs")
Ctry.Name<-read.csv(file.path(input,'Final Country Grid Col_Row Index.csv'))

@@

#read in mort data (created in the mortality timeseries chunk above)
mort_rate <- resp_mort_means_noage %>% 
  filter(Min.Year ==2020)
country_plot <- country_plot1 %>% left_join(mort_rate, by ='LocID')

# read in map data and align country names
worldData <- map_data("world")
#correct region names
worldData["region"][worldData["region"] == "Russia"] <- "Russian Federation"
worldData["region"][worldData["region"] == "USA"] <- "United States"
worldData["region"][worldData["region"] == "Virgin Islands" & worldData['subregion']==' US'] <- "US Virgin Islands"
worldData["region"][worldData["region"] == "Taiwan"] <- "China, Taiwan Province of China"
worldData["region"][worldData["region"] == "Trinidad" | worldData['region']=='Tobago'] <- "Trinidad and Tobago"
worldData["region"][worldData["region"] == "Grenadines"| worldData['region']=='Saint Vincent'] <- "Saint Vincent and the Grenadines"
worldData["region"][worldData["region"] == "Swaziland"] <- "Eswatini"
worldData["region"][worldData["region"] == "UK"] <- "United Kingdom"
worldData["region"][worldData["region"] == "Cape Verde"] <- "Cabo Verde"
worldData["region"][worldData["region"] == "Republic of Congo"] <- "Congo"
worldData["region"][worldData["region"] == "Democratic Republic of the Congo"] <- "Congo DRC"
worldData["region"][worldData["region"] == "Ivory Coast"] <- "Cote d'Ivoire"
worldData["region"][worldData["region"] == "Brunei"] <- "Brunei Darussalam"
worldData["region"][worldData["region"] == "Antigua"| worldData['region']=='Barbuda'] <- "Antigua and Barbuda"
worldData["region"][worldData["region"] == "Palestine"] <- "Palestinian Territory"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Hong Kong'] <- "China, Hong Kong SAR"
worldData["region"][worldData["region"] == "China" & worldData['subregion']=='Macao'] <- "China, Macao SAR"
worldData["region"][worldData["region"] == "Guernsey"| worldData['region']=='Jersey'] <- "Channel Islands"

@@

#chloropleth of world Per capita deaths
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = death_percap),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Deaths Per Capita",
                       n.breaks=10.5,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       #values=rescale(c(-1,0,1)),
                       limits=c(#0,
                                min(MergedData$death_percap, na.rm=TRUE),
                                0.3),
                       labels = c('Minimum',rep('',8),'Maximum'))+
  theme_void()+
  theme(legend.position = 'right')+
  theme(legend.key.height = unit(0.5,'cm'),
        legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))
